Foreground Signatures and Mitigation in Neutral Hydrogen Power Spectra From The Reionization Epoch

### 2014-10-10 foreground_delay_spectrum_modeling.tex
From 5b726ca: ============
(*) Added space after degree symbol.
(*) Merged branch 'Steven' with 'master'
(*) Revised author list (removed Desh and Bryan) and rearranged affiliation ordering
From 5b726ca: ============

(*) Added space after degree symbol.

\def\RRI{\altaffilmark{5}}
\def\RRItxt{\altaffiltext{5}{Raman Research Institute, Bangalore 560080, India}}

\def\Curtin{\altaffilmark{6}}
\def\Curtintxt{\altaffiltext{6}{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}}

\def\USydney{\altaffilmark{7}}
\def\USydneytxt{\altaffiltext{7}{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}}

\def\CAASTRO{\altaffilmark{8}}
\def\CAASTROtxt{\altaffiltext{8}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\MIT{\altaffilmark{9}}
\def\MITtxt{\altaffiltext{9}{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}}

\def\CfA{\altaffilmark{10}}
\def\CfAtxt{\altaffiltext{10}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\UW{\altaffilmark{11}}
\def\UWtxt{\altaffiltext{11}{Department of Physics, University of Washington, Seattle, WA 98195, USA}}

\def\Victoria{\altaffilmark{12}}
\def\Victoriatxt{\altaffiltext{12}{School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{13}}
\def\UWisctxt{\altaffiltext{13}{Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{14}}
\def\UMichigantxt{\altaffiltext{14}{Department of Atmospheric, Oceanic and Space Sciences, University of Michigan, Ann Arbor, MI 48109, USA}}

\def\CASS{\altaffilmark{15}}
\def\CASStxt{\altaffiltext{15}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\Tata{\altaffilmark{16}}
\def\Tatatxt{\altaffiltext{16}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\NRAO{\altaffilmark{17}}
\def\NRAOtxt{\altaffiltext{17}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UMelbourne{\altaffilmark{18}}
\def\UMelbournetxt{\altaffiltext{18}{School of Physics, The University of Melbourne, Parkville, VIC 3010, Australia}}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
%% Supporting authors
% A.~P.~Beardsley\UW,
% J.~Pober\UW,
% I.~S.~Sullivan\UW,
%% Builders' list
G.~Bernardi\SKASA,
F.~Briggs\ANU,
R.~J.~Cappallo\Haystack, 
B.~E.~Corey\Haystack, 
A.~A.~Deshpande\RRI, 
D.~Emrich\Curtin,
B.~M.~Gaensler\USydney$^,$\CAASTRO, 
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
E.~Kratzenberg\Haystack, 
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
D.~Oberoi\Tata, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
T.~Prabu\RRI, 
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
and~MWA~EoR~members
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UWtxt
\RRItxt
\SKASAtxt
\ANUtxt
\Haystacktxt
\Curtintxt
\USydneytxt
\CAASTROtxt
\MITtxt
\CfAtxt
\Victoriatxt
\UWisctxt
\UMichigantxt
\CASStxt
\Tatatxt
\NRAOtxt
\UMelbournetxt

@@

The MWA was completed in 2012 and, after commissioning, began its EoR observing program in 2013. In its final configuration the MWA is a 128--tile interferometer array capable of observing a 30.72~MHz instantaneous band anywhere in the range 80--300~MHz. Each tile is a phased array of 16 dipoles, each in the shape of a bow--tie. This yields a primary field of view $\gtrsim$~20\arcdeg wide and multiple secondary lobes. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km \citep{bea12}. Here we focus on antenna spacings $|\overline{\mathbf{x}}| \le 200$~m (spatial scales relevant to reionization) and a frequency range 170--200~MHz. The center frequency of 185~MHz corresponds to a redshift, $z\simeq 6.68$.

@@

The MWA targets two primary low-foreground fields for reionization observations. Here, we focus on the field at RA = 0h, Dec = $-30$\arcdeg. The MWA tracks a patch of sky through antenna beams formed and steered electronically by controlling delay settings of the dipoles in an MWA tile. The pointing system is capable of steering to points on a regular $\sim$7\arcdeg grid. During observations we allow the sky to drift across the nearest available pointing, shifting between grid points as necessary (once in $\sim 30$~minutes). This process is repeated throughout the course of the observation $\approx 4.86$~hours. Figure~\ref{fig:pointings} illustrates how the apparent pointing oscillates around the desired pointing direction.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/custom_pointings.eps}
\caption{MWA tile beam pointing directions during the course of the observation. The $x$--axis refers to the {\it local sidereal time} (LST). The axis on the left refers to longitudes, namely, Right Ascension (RA) and Hour Angle (HA). Negative values of RA, HA, and LST are to be interpreted as having been wrapped around by 360\arcdeg or 24 hours. The axis on the right refers to the declination of the pointing direction. The RA, HA, and declination are plotted with solid, dashed and dotted lines respectively. The sky is allowed to drift for $\sim 30$~mins before the beamformer delay settings change in a discrete step to center the beam around RA = 0h, Dec = $-30$\arcdeg. Dot--dashed vertical lines show the LST of {\it off-zenith} and {\it zenith} pointings used in our study. \label{fig:pointings}}
\end{figure}

@@

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al. 2014, submitted). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning; it has a flux density limit of 25~mJy and a declination range of -12\arcdeg to -40\arcdeg evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm -- based on forward modeling software by \citet{sul12} -- computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antennas to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variations in cable delay. Finally, we fit for an additional phase known to be caused by reflections in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

The MWA has a very wide field of view ($\gtrsim 20$\arcdeg at 185~MHz) and has non--zero response all the way to the horizon. As already noted, foreground objects fill the {\it foreground wedge} with an amplitude which depends on the tile power gain in that direction, with objects at the horizon being closest to the boundaries of the {\it wedge}.

@@

We use a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz to provide our compact object catalog due to their complementary survey footprints covering the entire sky, and matched flux density sensitivity and angular resolution. The SUMSS catalog covers the sky with declination $\delta < -30$\arcdeg with a limiting peak brightness of 6--10~mJy/beam and an angular resolution of $\sim 45$\arcsec. The NVSS covers the sky with $\delta > -40$\arcdeg with a similar angular resolution and a limiting flux density of $\approx 2.5$~mJy for compact objects.

@@

This screening technique can be customized when it is necessary to optimize between foreground mitigation and loss of sensitivity from discarding data. Figure~\ref{fig:screening} shows how the typical foreground contamination in the {\it EoR window} depends on the orientations and lengths of discarded antenna spacings. We choose antenna spacings oriented eastward to varying degrees of directedness, i.e., -7\fdg 5~$\le\theta_\textrm{b}<$~7\fdg 5 (solid circles), -15\arcdeg~$\le\theta_\textrm{b}<$~15\arcdeg (solid squares), and -22\fdg 5~$\le\theta_\textrm{b}<$~22\fdg 5 (solid stars). Among antenna spacings that satisfy these criteria, we discard data from those whose lengths are shorter than $|\overline{\mathbf{x}}|_\textrm{max}$ ($x$--axis) and show foreground contamination estimated in the {\it EoR window} from all remaining antenna spacings. Foreground contamination estimated from only northward (dashed line) and eastward (dot--dashed line) antenna spacings represent the lower and upper limits, respectively, and are shown for reference. It is seen that foreground contamination can be mitigated by a factor between $\sim 1.5$ ($|\theta_\textrm{b}|\le$~7\fdg 5) and $\sim 10$ ($|\theta_\textrm{b}|\le$~22\fdg 5). It is notable that short antenna spacings play maximum role in determining foreground contamination. For instance, among antenna spacings with orientations $|\theta_\textrm{b}|\le$~22\fdg 5, discarding those with lengths $|\overline{\mathbf{x}}|>40$~m has no effect on further foreground contamination and would only lead to loss of sensitivity. On the other hand, a bright compact object at the same location will give rise to foreground contamination even on longer antenna spacings. Such cases will necessitate discarding more or all of the eastward oriented antenna spacings.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_nside_64_Tsys_95.0K.eps}
\caption{Foreground contamination in {\it EoR window} for the {\it off--zenith} pointing as a function of orientation and length of discarded antenna spacings. Antenna spacings oriented eastward with varying degrees of directedness are considered: -7\fdg 5~$\le\theta_\textrm{b}<$~7\fdg 5 (solid circles), -15\arcdeg~$\le\theta_\textrm{b}<$~15\arcdeg (solid squares), and -22\fdg 5~$\le\theta_\textrm{b}<$~22\fdg 5 (solid stars). Among antenna spacings that satisfy the above criteria, ones with lengths $\le |\overline{\mathbf{x}}|_\textrm{max}$ ($x$--axis) are discarded. Lower (dashed line) and upper (dot--dashed) limits on foreground contamination are derived from northward (67\fdg 5~$\le\theta_\textrm{b}<$~112\fdg 5) and eastward ($|\theta_\textrm{b}|\le$~22\fdg 5) antenna spacings respectively. Foreground contamination in the {\it EoR window} reduces by factor $\sim$1.5 ($|\theta_\textrm{b}|\le$~7\fdg 5) to $\sim$10 ($|\theta_\textrm{b}|\le$~22\fdg 5). Short baselines have maximum effect on foreground contamination. For instance, discarding antenna spacings oriented $|\theta_\textrm{b}|\le$~22\fdg 5 with lengths $|\overline{\mathbf{x}}|>40$~m has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}

>>>>

\def\Curtin{\altaffilmark{5}}
\def\Curtintxt{\altaffiltext{5}{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}}

% \def\USydney{\altaffilmark{7}}
% \def\USydneytxt{\altaffiltext{7}{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}}

\def\MIT{\altaffilmark{6}}
\def\MITtxt{\altaffiltext{6}{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}}

\def\CfA{\altaffilmark{7}}
\def\CfAtxt{\altaffiltext{7}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\UW{\altaffilmark{8}}
\def\UWtxt{\altaffiltext{8}{Department of Physics, University of Washington, Seattle, WA 98195, USA}}

\def\Victoria{\altaffilmark{9}}
\def\Victoriatxt{\altaffiltext{9}{School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{10}}
\def\UWisctxt{\altaffiltext{10}{Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{11}}
\def\UMichigantxt{\altaffiltext{11}{Department of Atmospheric, Oceanic and Space Sciences, University of Michigan, Ann Arbor, MI 48109, USA}}

\def\CASS{\altaffilmark{12}}
\def\CASStxt{\altaffiltext{12}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\CAASTRO{\altaffilmark{13}}
\def\CAASTROtxt{\altaffiltext{13}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\Tata{\altaffilmark{14}}
\def\Tatatxt{\altaffiltext{14}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\RRI{\altaffilmark{15}}
\def\RRItxt{\altaffiltext{15}{Raman Research Institute, Bangalore 560080, India}}

\def\NRAO{\altaffilmark{16}}
\def\NRAOtxt{\altaffiltext{16}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UMelbourne{\altaffilmark{17}}
\def\UMelbournetxt{\altaffiltext{17}{School of Physics, The University of Melbourne, Parkville, VIC 3010, Australia}}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
%% Supporting authors
% A.~P.~Beardsley\UW,
% J.~Pober\UW,
% I.~S.~Sullivan\UW,
%% Builders' list
G.~Bernardi\SKASA,
F.~Briggs\ANU,
R.~J.~Cappallo\Haystack, 
B.~E.~Corey\Haystack, 
% A.~A.~Deshpande\RRI, 
D.~Emrich\Curtin,
% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
E.~Kratzenberg\Haystack, 
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
D.~Oberoi\Tata, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
T.~Prabu\RRI, 
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
and~MWA~EoR~members
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\SKASAtxt
\ANUtxt
\Haystacktxt
\Curtintxt
% \USydneytxt
\MITtxt
\CfAtxt
\UWtxt
\Victoriatxt
\UWisctxt
\UMichigantxt
\CASStxt
\CAASTROtxt
\Tatatxt
\RRItxt
\NRAOtxt
\UMelbournetxt

@@

The MWA was completed in 2012 and, after commissioning, began its EoR observing program in 2013. In its final configuration the MWA is a 128--tile interferometer array capable of observing a 30.72~MHz instantaneous band anywhere in the range 80--300~MHz. Each tile is a phased array of 16 dipoles, each in the shape of a bow--tie. This yields a primary field of view $\gtrsim$~20\arcdeg~ wide and multiple secondary lobes. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km \citep{bea12}. Here we focus on antenna spacings $|\overline{\mathbf{x}}| \le 200$~m (spatial scales relevant to reionization) and a frequency range 170--200~MHz. The center frequency of 185~MHz corresponds to a redshift, $z\simeq 6.68$.

@@

The MWA targets two primary low-foreground fields for reionization observations. Here, we focus on the field at RA = 0h, Dec = $-30$\arcdeg. The MWA tracks a patch of sky through antenna beams formed and steered electronically by controlling delay settings of the dipoles in an MWA tile. The pointing system is capable of steering to points on a regular $\sim$7\arcdeg~ grid. During observations we allow the sky to drift across the nearest available pointing, shifting between grid points as necessary (once in $\sim 30$~minutes). This process is repeated throughout the course of the observation $\approx 4.86$~hours. Figure~\ref{fig:pointings} illustrates how the apparent pointing oscillates around the desired pointing direction.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/custom_pointings.eps}
\caption{MWA tile beam pointing directions during the course of the observation. The $x$--axis refers to the {\it local sidereal time} (LST). The axis on the left refers to longitudes, namely, Right Ascension (RA) and Hour Angle (HA). Negative values of RA, HA, and LST are to be interpreted as having been wrapped around by 360\arcdeg~ or 24 hours. The axis on the right refers to the declination of the pointing direction. The RA, HA, and declination are plotted with solid, dashed and dotted lines respectively. The sky is allowed to drift for $\sim 30$~mins before the beamformer delay settings change in a discrete step to center the beam around RA = 0h, Dec = $-30$\arcdeg. Dot--dashed vertical lines show the LST of {\it off-zenith} and {\it zenith} pointings used in our study. \label{fig:pointings}}
\end{figure}

@@

The data are flagged\footnote{\url{http://sourceforge.net/p/aoflagger}} for interference \citep{off12,off10}, removing 3\% of the data and averaged in time  and frequency from the raw 0.5~s, 40~kHz to 2s, 80~kHz. These data are then calibrated to a simulation of the sky containing 2420 point--like objects selected from the MWA Commissioning Survey (MWACS; Hurley-Walker et al. 2014, submitted). MWACS was compiled using observations taken with subsets of the array during the final buildout and commissioning; it has a flux density limit of 25~mJy and a declination range of -12\arcdeg~ to -40\arcdeg~ evenly covering the field of view of the observations reported here. The objects used in calibration are selected to lie inside the 5\% contour of the primary lobe of the tile power--pattern. The calibration algorithm -- based on forward modeling software by \citet{sul12} -- computes complex gain solutions per channel per antenna averaged to two minute intervals. The solutions are fairly low signal--to--noise so we iteratively project along the antenna and frequency dimensions to capture the relatively independent passband and antenna--to--antenna variation. First, we average the channel gains over all antennas to obtain a high signal--to--noise measurement of the bandpass. After applying this single passband, we do a second round of calibration and fit second and first order polynomials for amplitude and phase respectively for each antenna. This flattens any residual variation in bandpass and removes small phase slopes due to variations in cable delay. Finally, we fit for an additional phase known to be caused by reflections in 150~m length cables. %possibly could add elaboration, if I knew exactly which version of the cal was done here. doesn't really matter

@@

The MWA has a very wide field of view ($\gtrsim 20$\arcdeg~ at 185~MHz) and has non--zero response all the way to the horizon. As already noted, foreground objects fill the {\it foreground wedge} with an amplitude which depends on the tile power gain in that direction, with objects at the horizon being closest to the boundaries of the {\it wedge}.

@@

We use a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz to provide our compact object catalog due to their complementary survey footprints covering the entire sky, and matched flux density sensitivity and angular resolution. The SUMSS catalog covers the sky with declination $\delta < -30$\arcdeg~ with a limiting peak brightness of 6--10~mJy/beam and an angular resolution of $\sim 45$\arcsec. The NVSS covers the sky with $\delta > -40$\arcdeg~ with a similar angular resolution and a limiting flux density of $\approx 2.5$~mJy for compact objects.

@@

This screening technique can be customized when it is necessary to optimize between foreground mitigation and loss of sensitivity from discarding data. Figure~\ref{fig:screening} shows how the typical foreground contamination in the {\it EoR window} depends on the orientations and lengths of discarded antenna spacings. We choose antenna spacings oriented eastward to varying degrees of directedness, i.e., -7\fdg 5~$\le\theta_\textrm{b}<$~7\fdg 5 (solid circles), -15\arcdeg~$\le\theta_\textrm{b}<$~15\arcdeg~ (solid squares), and -22\fdg 5~$\le\theta_\textrm{b}<$~22\fdg 5 (solid stars). Among antenna spacings that satisfy these criteria, we discard data from those whose lengths are shorter than $|\overline{\mathbf{x}}|_\textrm{max}$ ($x$--axis) and show foreground contamination estimated in the {\it EoR window} from all remaining antenna spacings. Foreground contamination estimated from only northward (dashed line) and eastward (dot--dashed line) antenna spacings represent the lower and upper limits, respectively, and are shown for reference. It is seen that foreground contamination can be mitigated by a factor between $\sim 1.5$ ($|\theta_\textrm{b}|\le$~7\fdg 5) and $\sim 10$ ($|\theta_\textrm{b}|\le$~22\fdg 5). It is notable that short antenna spacings play maximum role in determining foreground contamination. For instance, among antenna spacings with orientations $|\theta_\textrm{b}|\le$~22\fdg 5, discarding those with lengths $|\overline{\mathbf{x}}|>40$~m has no effect on further foreground contamination and would only lead to loss of sensitivity. On the other hand, a bright compact object at the same location will give rise to foreground contamination even on longer antenna spacings. Such cases will necessitate discarding more or all of the eastward oriented antenna spacings.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_nside_64_Tsys_95.0K.eps}
\caption{Foreground contamination in {\it EoR window} for the {\it off--zenith} pointing as a function of orientation and length of discarded antenna spacings. Antenna spacings oriented eastward with varying degrees of directedness are considered: -7\fdg 5~$\le\theta_\textrm{b}<$~7\fdg 5 (solid circles), -15\arcdeg~$\le\theta_\textrm{b}<$~15\arcdeg~ (solid squares), and -22\fdg 5~$\le\theta_\textrm{b}<$~22\fdg 5 (solid stars). Among antenna spacings that satisfy the above criteria, ones with lengths $\le |\overline{\mathbf{x}}|_\textrm{max}$ ($x$--axis) are discarded. Lower (dashed line) and upper (dot--dashed) limits on foreground contamination are derived from northward (67\fdg 5~$\le\theta_\textrm{b}<$~112\fdg 5) and eastward ($|\theta_\textrm{b}|\le$~22\fdg 5) antenna spacings respectively. Foreground contamination in the {\it EoR window} reduces by factor $\sim$1.5 ($|\theta_\textrm{b}|\le$~7\fdg 5) to $\sim$10 ($|\theta_\textrm{b}|\le$~22\fdg 5). Short baselines have maximum effect on foreground contamination. For instance, discarding antenna spacings oriented $|\theta_\textrm{b}|\le$~22\fdg 5 with lengths $|\overline{\mathbf{x}}|>40$~m has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}
